Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
update for Pierce lighning talk

How open is open source? Open software needs a diverse, openly governed
community behind it, just as it needs open licensing and a public code
repository. To probe the level of governance within open source projects, we
suggest a contest to encourage individual developers to submit patches and pull
request to projects that are important to them. This simple mechanism will
expose several governance mechanisms, such as how easy it is for independent
developers to communicate with project leadership, how projects accept and
properly license third party contributions, and how projects make decisions such
as granting source tree write access.

>>>>

Pierce discussed how open open source is. Open software needs a diverse, openly governed
community behind it, just as it needs open licensing and a public code
repository. To probe the level of governance within open source projects, he and
his co-authors (Suresh Marru and Chris Mattman)
suggested a contest to encourage individual developers to submit patches and pull
request to projects that are important to them. This simple mechanism will
expose several governance mechanisms, such as how easy it is for independent
developers to communicate with project leadership, how projects accept and
properly license third party contributions, and how projects make decisions such
as granting source tree write access.
